---
title: "Testing Python"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
library(tidyverse)
```

## Python in `.Rmd` files

### Load libraries

Just like R, you can use Python in `.Rmd` files! Here we import our libraries

```{python libraries}
import pandas as pd
```

### Load data

Let's load the titanic data and view the top of the data set:

```{python data}
titanic  = pd.read_csv("../data/titanic.csv")
titanic.head()
```

### plot data

I currently cannot make altair work in `.Rmd` chunks, but it doens't bother me so much given that I can pass the python data frame into `ggplot` using `py$data_frame` syntax 🤷.

```{r plot, warning=FALSE, fig.height=4, fig.width=4}
ggplot2::ggplot(py$titanic, aes(x = age, y = fare)) +
  geom_point()
```

### And inline python code within markdown text!

Here we find the destination of the first passenger:

```{python first destination}
first_dest = titanic["home.dest"][0]
```

The destination of the first passenger is `r py$first_dest`.